%-------------------------
% Resume in Latex
% Author : Matthew Juhasz
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
%vspace removes the white space between the sections.  make tighter if low on space.  
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-12pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%--------------RESUME STARTS HERE-----------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Matthew Juhasz} \\
    \small{Aurora, ON} $|$
    \small 647-574-4206 $|$ \href{mailto:matthew.a.juhasz@gmail.com}{\underline{matthew.a.juhasz@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/matthew-juhasz}{\underline{linkedin.com/in/matthew-juhasz}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto St. George}{Sept. 2019 -- June 2023}
      {\textbf {Honours Bachelor of Science} -- \textit{With High Distinction}}{}
      \resumeItemListStart
        \resumeItem{Major in Human Biology -- Neuroscience, with Minor's in Physiology \& Psychology}
        \resumeItem{Victoria College Regents In-Course Scholarship}
        \resumeItem{Dean’s List Scholar for Summer of 2020, Summer of 2021, Winter of 2023}
           \resumeItem{The Rakoczi Prize in Hungarian Studies 2021-2022}
      \resumeItemListEnd
      \resumeSubHeadingListEnd



%-----------EXPERIENCE Section-----------
\section{Experience}
  \resumeSubHeadingListStart
     
%-----------PPPC Experience Subheading-----------
    \resumeSubheading
      {Administrative Assistant}{March 2018 -- August 2022}
      {Pilowsky Professional Psychology Corporation}{Etobicoke}
      \resumeItemListStart
        \resumeItem{Direct assistant to Dr. Pilowsky, responsible for drafting documents, forwarding patient calls, and scheduling patient appointments in accordance with Dr. Pilowsky's schedule. }
        \resumeItem{General clerical duties, including file creation and management on the \textit{File Management System} software.}
        \resumeItem{Assisted in bookkeeping records and managed bills payable, meticulously tallying incoming payments while crosschecking \textit{QuickBooks}. Handled bank deposits during the bookkeeper’s absence.}
        \resumeItem{Engaged directly with patients with intake screenings and phone call appointment reminders.}
      \resumeItemListEnd
    %-----------RP Experience Subheading-----------
    \resumeSubheading
      {Operations and Ambassador Program Manager}{Oct 2023 -- Current}
      {Retaliation Project}{Toronto}
      \resumeItemListStart
        \resumeItem{Collaborate with brand owners to navigate logistical challenges, providing support ranging from budgeting, \linebreak to product manufacturing and fulfillment delays.}
        \resumeItem{Personally overseeing bi-weekly inventory ordering with totals of up to \$100'000 USD, while ensuring accurate estimation of the required ``extra/on-hand'' stock until next orders.}
        \resumeItem{Successfully oversee the Retaliation Project ``Ambassador Program'', ensuring the fulfillment of social media posting quotas of 75+ Brand Ambassadors through weekly communication.}
        \resumeItem{Proficiently manage inventory, maintain and update website, and ensure seamless end-to-end order processing on the back-end \textit{Shopify} platform.}
        \resumeItem{Deliver exceptional customer service while maintaining professionalism; especially during conflict mitigation.}
        \resumeItem{Playing a pivotal role in enhancing overall operational efficiency, showcasing adaptability and resourcefulness in a dynamic 1st year-startup environment.}

      \resumeItemListEnd
    %-----------SMH Experience Subheading-----------
    \resumeSubheading
      {Volunteer Research Assistant}{June 2022 -- Current}
      {St. Michael's Hospital, Keenan Research Centre for Biomedical Science}{Toronto}
        \resumeItemListStart
            \resumeItem{Integral involvement in the scientific writing process, contributing significantly to the formulation and editing of a manuscript titled ``Inner Dialogue Dysfunction and the Abusive Comments of the Dominant Hemisphere'' for the esteemed peer-reviewed scientific journal, Neurocase.}
            \resumeItem{Diligently accessed, summarized, presented, and maintained confidential Personal Health Information via Unity Health’s Soarian Clinicals Database and the SMH Memory Clinic Excel Database.}
            \resumeItem{Collaborated with research team to identify data of interest and irrelevant or redundant data, followed by the amendment of intake questionnaires and consent forms.}
            \resumeItem{Implementing database alterations to extract, interpret, and visually represent data tailored to the specific needs of ongoing research projects.}
        \resumeItemListEnd

%-----------End of SubHeading List for Experience Section-------- %
    
    \resumeSubHeadingListEnd
    
%-----------SKILLS-----------
\section{Skills}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Soft Skills} $|$ \emph{Developed through the Royal Canadian Army Cadets and Professional Experience}}{}
          \resumeItemListStart
                \resumeItem{Highly organized and competent at various forms of data, file, and information management, especially with confidential information.}
                \resumeItem{Proficient in effectively communicating and presenting complex topics while maintaining clarity.}
                \resumeItem{Excellent critical thinking and decision-making skills, even under high-stress conditions.}
                \resumeItem{Exemplary work ethic and punctuality, with consistent and timely delivery of high-quality results.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Hard Skills} $|$ \emph{Developed through Projects and work-place training}}{}
          \resumeItemListStart
              \resumeItem{Software: Microsoft Office \& Google Suite, QuickBooks, Shopify, Soarian Clinicals Database, BioPac, BrainStorm.}
              \resumeItem {Programming Languages: Back-end Python, Git and GitHub, LaTeX.}
              \resumeItem {3 Years of Laboratory Experience exemplifying precision, organization, and attention to detail.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
\end{document}

%------------------END OF DOCUMENT-------------------------








    
%-----------Cadets Section-----------
\section{Royal Canadian Army Cadets}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Responsibilities} $|$ \emph{At the 37 Parkside Drive Armoury}}{January 2015 to June 2018}
          \resumeItemListStart
            \resumeItem{Weekly Parades on Tuesday Nights, with weekend training exercise and weekend team training. }
            \resumeItem{Full Time 3rd year cadet Instructor for 2017/2018 Year.  Create lesson plans and teach curriculum material to youth aged 14-15, in addition to supervision of the group of 20 during parade nights and weekend exercises}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Achievements}}{}
          \resumeItemListStart
            \resumeItem{Successfully completed the "Drill and Ceremonial Instructor" course and Standard First Aid Qualification during the summer of 2016 in Alpha Company, at Black Down Cadet Training Center, Base Borden Ontario}
            \resumeItem{Appointed parade position of Senior Rifleman of the 2016/2017 home corps Flag Party Top Gold Star Cadet
Award 2017}
            \resumeItem{National Star of Excellence 2017}
            \resumeItem{Achieved rank of Cadet Warrant Officer in June 2017}
            \resumeItem{Successfully completed "Leadership and Challenge" course during the summer of 2017 in 3 Platoon at Rocky Mountain Cadet Training
Center, Cochrane, Alberta}
            \resumeItem{Appointed parade position of Senior Flag Bearer of the 2017 Rocky Mountain Cadet Training Center Flag Party}
            \resumeItem{Successfully completed the \textit{Trillium Regional Expedition} }
            \resumeItem{Appointed parade position of Senior Flag Bearer of the 2017/2018 home corps Flag Party}
            \resumeItem{3rd Place at regional Orienteering competition Fall 2018}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


